---
title: "Preprocessing Stats from `r participant`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center')
options(width = 1200)
library(kableExtra)
library(ggpubr)
library(scales)
library(plotly)
library(tidyverse)

c.theme <- function(){
  theme_minimal() +
    theme(text = element_text(family = 'serif'),
          plot.title = element_text(hjust = 0.5, size = 20),
          axis.title = element_text(size = 14),
          axis.text = element_text(size = 12),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14))
}
```

## General Tracking Information

```{r, include = FALSE}
perc_tracked_block <- combined_n %>%
  filter(block != 'instructions') %>%
  mutate(block = fct_drop(block)) %>%
  group_by(trials_this_n, block) %>%
  summarize(n = n(),
            tracked = sum(!is.na(average_gaze_x) & !is.na(average_gaze_y)),
            perc = round(tracked/n()*100,2)) %>%
  ungroup() %>%
  complete(trials_this_n,block)

perc_tracked_overall <- combined_n %>%
  filter(block != 'instructions') %>%
  summarize(n = n(),
            tracked = sum(!is.na(average_gaze_x) & !is.na(average_gaze_y)),
            perc = round(tracked/n()*100,2),
            )

missing_blocks <- perc_tracked_block %>%
  filter(is.na(perc))
```

Overall, `r perc_tracked_overall$perc`% of samples had a recorded gaze position.

The total number of blocks in this design was `r nlevels(perc_tracked_block$trials_this_n) * nlevels(perc_tracked_block$block)`. This was calculated as the number of trials multiplied by the number of blocks within each trial.

Out of those blocks, `r nrow(missing_blocks)` were completely missing data. These missing blocks can be seen below:

<center>

```{r print missing blocks}
missing_blocks %>%
  kable %>%
  kable_styling("striped") %>% 
  scroll_box(width = "500px", height = "100px")
```

</center>


The percent of samples tracked within each block can be seen below:

<center>

```{r print percent tracked}
perc_tracked_block %>%
  kable %>%
  kable_styling("striped") %>% 
 scroll_box(width = "500px", height = "200px")
```

</center>

### Gaze Position

```{r}
perc_on_screen <- combined_n %>%
  filter(block != 'instructions', !is.na(average_gaze_x),!is.na(average_gaze_y)) %>%
  summarize(avg_within = round(sum(between(average_gaze_x,0,1920) & between(average_gaze_y,0,1080))/n()*100,2))

perc_in_stim <- combined_n %>%
  filter(block == 'stimulus', !is.na(average_gaze_x), !is.na(average_gaze_y)) %>%
  summarize(avg_within = round(sum(between(average_gaze_x,540,1380) & between(average_gaze_y,270,810))/n()*100,2))
```

All gaze position data is taken after the instructions were completed. Presented data is average gaze position as given by the eyetracker. Samples where no eyetracking data is recorded are removed from the overall count.

- % of time participant was gazing on screen: `r perc_on_screen$avg_within`%.

<center>

```{r screen gaze position}
screen_gaze_hist <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920) & between(average_gaze_y,0,1080)) %>%
  select(average_gaze_x, average_gaze_y) %>%
  ggplot(aes(x = average_gaze_x, average_gaze_y, fill = ..count../sum(..count..)*100,
             text = after_stat(paste('x:', round(x,0), '\n',
                                     'y:', round(-y,0), '\n',
                                     'percent:', round(count/sum(count)*100,2),'%')))) +
  geom_hex() +
  scale_x_continuous(limits = c(0,1920)) +
  scale_y_reverse(limits = c(1080,0)) +
  scale_fill_viridis_c(option = 'inferno', limits = c(0,5), oob = squish) +
  coord_fixed() +
  labs(title = 'Gaze Plot Over the Screen', x = '', y = '', fill = '% of samples') +
  c.theme()

ggplotly(screen_gaze_hist, tooltip = 'text')
```

</center>

- % of time participant was gazing within the stimulus area during stimulus blocks: `r perc_in_stim$avg_within`%.

<center>

```{r stim gaze position}
stim_gaze_hist <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  select(average_gaze_x, average_gaze_y) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, fill = ..count../sum(..count..)*100,
             text = after_stat(paste('x:', round(x,0), '\n',
                                     'y:', round(-y,0), '\n',
                                     'percent:', round(count/sum(count)*100,2),'%')))) +
  geom_hex() +
  scale_y_reverse() +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(0,5), oob = squish) +
  labs(title = 'Gaze Within Stimulus Zone During Stimulus', x = '', y = '', fill = '% of samples') +
  c.theme()

ggplotly(stim_gaze_hist, tooltip = list('x','y','text'))
```

</center>

## Pupil Size

### Distribution of Pupil Sizes

Eyelink reports pupil data from left and right eyes as well as the average of the two. The preprocessing pipeline performs mean and median normalization on all 3 measures relative to prefixation and fixation baselines. The following plots show the distribution of pupil sizes for samples where the participant has their gaze on the screen during the experiment (i.e. past the instructions block).

```{r pupil size histograms}
pupil_dens <- function(df,plot_title){
  df %>%
    pivot_longer(everything(),
                 names_to = 'type',
                 values_to = 'size') %>%
    mutate(type = str_extract(type,c('average','left','right'))) %>%
    ggplot(aes(x = size, fill = type)) +
    geom_density(alpha = .3) +
    labs(x = 'Pupil Size', y = '', title = plot_title, fill = 'Eye') +
    c.theme() +
    theme(plot.title = element_text(size = 14),
          axis.title = element_text(size = 12))
}

raw_p <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920), between(average_gaze_y,0,1080)) %>%
  select(c(average_pupil_size,left_pupil_size,right_pupil_size)) %>%
  pupil_dens(plot_title = 'Raw Pupil Size')

med_pf_p <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920), between(average_gaze_y,0,1080)) %>%
  select(c(med_average_pupil_norm_pf, med_left_pupil_norm_pf, med_right_pupil_norm_pf)) %>%
  pupil_dens(plot_title = 'Median Prefix Normalized Pupil Size')

med_fix_p <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920), between(average_gaze_y,0,1080)) %>%
  select(c(mean_average_pupil_norm_pf, mean_left_pupil_norm_pf, mean_right_pupil_norm_pf)) %>%
  pupil_dens(plot_title = 'Mean Prefix Normalized Pupil Size')

mean_pf_p <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920), between(average_gaze_y,0,1080)) %>%
  select(c(med_average_pupil_norm_fix, med_left_pupil_norm_fix, med_right_pupil_norm_fix)) %>%
  pupil_dens(plot_title = 'Median Fixation Normalized Pupil Size')

mean_fix_p <- combined_n %>%
  filter(block != 'instructions', between(average_gaze_x,0,1920), between(average_gaze_y,0,1080)) %>%
  select(c(mean_average_pupil_norm_fix, mean_left_pupil_norm_fix, mean_right_pupil_norm_fix)) %>%
  pupil_dens(plot_title = 'Mean Fixation Normalized Pupil Size')

ggarrange(med_pf_p, med_fix_p, mean_pf_p, mean_fix_p, raw_p, 
                       ncol = 2,
                       nrow = 3,
                       common.legend = TRUE)
```

### Pupil Sizes During Stimuli

#### Epoch Median

Median average (combined left and right values) pupil size is plotted for each stimulus block as a function of epoch. Raw values are plotted followed by prefixation and fixation-normalized values, respectively. Within stimulus blocks, patterns of change in pupil size are not different across the raw and two types of normalization, however the differences pupil size between blocks does differ across normalizations. The extent to which they differ is dependent on the variance in pupil size during the chosen normalization block across samples.

```{r raw stimuli pupil sizes, fig.width = 12, fig.height= 8}
stim_df %>%
  ggplot(aes(x = epoch, y = stim_med_average_pupil_size)) +
  geom_point(size = 2) + 
  facet_wrap(~trials_this_n) + 
  labs(x = 'Epoch', y = 'Pupil Size (unitless)', title = 'Raw Median Pupil Size Across Epochs Within Stimulus') +
  c.theme()
```

```{r pf norm stimuli pupil sizes, fig.width = 12, fig.height= 8}
stim_df %>%
  ggplot(aes(x = epoch, y = stim_med_average_pupil_norm_pf)) +
  geom_point(size = 2) + 
  facet_wrap(~trials_this_n) + 
  labs(x = 'Epoch', y = 'Pupil Size (unitless)', title = 'Prefixation-normalized Median Pupil Size Across Epochs Within Stimulus') +
  c.theme()
```

```{r fix norm stimuli pupil sizes, fig.width = 12, fig.height= 8}
stim_df %>%
  ggplot(aes(x = epoch, y = stim_med_average_pupil_norm_fix)) +
  geom_point(size = 2) + 
  facet_wrap(~trials_this_n) + 
  labs(x = 'Epoch', y = 'Pupil Size (unitless)', title = 'Prefixation-normalized Median Pupil Size Across Epochs Within Stimulus') +
  c.theme()
```


### Pupil Size and Gaze Position

Median average pupil size are plotted as functions of gaze position during stimulus blocks. Only positions within the boundary of the stimulus area are plotted. Non-normalized median values are plotted first followed by prefixation normalized, and then fixation normalized.

#### Raw Pupil Size

<center>

```{r raw pupil size gaze, fig.show='hold'}
stim_gaze_pupil_size <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = average_pupil_size)) +
  stat_summary_hex(fun = 'median', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno',limits = c(300,550), oob = squish) +
  labs(title = 'Median Average Pupil Size', x = '', y = '', fill = 'Average Pupil Size') +
  c.theme()

stim_gaze_pupil_sd <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = average_pupil_size)) +
  stat_summary_hex(fun = 'sd', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(0,100), oob = squish) +
  labs(title = 'Median Average Pupil SD', x = '', y = '', fill = 'Average Pupil SD') +
  c.theme()

stim_gaze_pupil_n <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  select(average_gaze_x, average_gaze_y) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, fill = ..count..,
             text = after_stat(paste('x:', round(x,0), '\n',
                                     'y:', round(-y,0), '\n',
                                     'n:', count)))) +
  geom_hex() +
  scale_y_reverse() +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(0,500), oob = squish) +
  labs(title = 'Total Samples Samples', x = '', y = '', fill = 'N') +
  c.theme()

ggplotly(stim_gaze_pupil_size)

ggplotly(stim_gaze_pupil_sd)

ggplotly(stim_gaze_pupil_n, tooltip = c('text'))
```

</center>

#### Prefixation Normalized 

<center>

```{r, fig.show='hold'}
stim_gaze_pupil_size_pf <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = med_average_pupil_norm_pf)) +
  stat_summary_hex(fun = 'median', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Prefixation Normalized Median Pupil Size', x = '', y = '', fill = 'Average Pupil Size') +
  c.theme()

stim_gaze_pupil_sd_pf <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = med_average_pupil_norm_pf)) +
  stat_summary_hex(fun = 'sd', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Prefixation Normalized Median Pupil SD', x = '', y = '', fill = 'Average Pupil SD') +
  c.theme()

ggplotly(stim_gaze_pupil_size_pf)

ggplotly(stim_gaze_pupil_sd_pf)

```

</center>

#### Fixation Normalized 

<center>

```{r, fig.show='hold'}
stim_gaze_pupil_size_fix <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = med_average_pupil_norm_fix)) +
  stat_summary_hex(fun = 'median', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Fixation Normalized Median Pupil Size', x = '', y = '', fill = 'Average Pupil Size') +
  c.theme()

stim_gaze_pupil_sd_fix <- combined_n %>%
  filter(block == 'stimulus', between(average_gaze_x,540,1380) & between(average_gaze_y,270,810)) %>%
  ggplot(aes(x = average_gaze_x, y = average_gaze_y, z = med_average_pupil_norm_fix)) +
  stat_summary_hex(fun = 'sd', fun.args = list(na.rm = TRUE)) +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(810,270)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Fixation Normalized Median Pupil SD', x = '', y = '', fill = 'Average Pupil SD') +
  c.theme()

ggplotly(stim_gaze_pupil_size_fix)

ggplotly(stim_gaze_pupil_sd_fix)

```

</center>