---
title: "Preprocessing Stats from `r participant`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center')
options(width = 1200)
library(kableExtra)
library(ggpubr)
library(scales)
library(hexbin)
library(plotly)
library(tidyverse)

c.theme <- function(){
  theme_minimal() +
    theme(text = element_text(family = 'serif'),
          plot.title = element_text(hjust = 0.5, size = 20),
          axis.title = element_text(size = 14),
          axis.text = element_text(size = 12),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14))
}
```

## General Tracking Information

```{r, include = FALSE}
perc_tracked_block <- combined_n %>%
  filter(block != 'response') %>%
  mutate(block = fct_drop(block)) %>%
  group_by(remember_loop_this_trial_n, block) %>%
  summarize(n = n(),
            tracked = sum(!is.na(comb_gaze_x) & !is.na(comb_gaze_y)),
            perc = round(tracked/n()*100,2)) %>%
  ungroup() %>%
  complete(remember_loop_this_trial_n,block)

perc_tracked_overall <- combined_n %>%
  filter(block != 'response') %>%
  summarize(n = n(),
            tracked = sum(!is.na(comb_gaze_x) & !is.na(comb_gaze_y)),
            perc = round(tracked/n()*100,2),
            )

missing_blocks <- perc_tracked_block %>%
  filter(is.na(perc))
```

Overall, `r perc_tracked_overall$perc`% of samples had a recorded gaze position.

The total number of blocks in this design was `r nlevels(perc_tracked_block$remember_loop_this_trial_n) * nlevels(perc_tracked_block$block)`. This was calculated as the number of trials multiplied by the number of blocks within each trial.

Out of those blocks, `r nrow(missing_blocks)` were completely missing data. These missing blocks can be seen below:

<center>

```{r print missing blocks}
missing_blocks %>%
  rename(trial = remember_loop_this_trial_n) %>%
  kable %>%
  kable_styling("striped") %>% 
  scroll_box(width = "500px", height = "100px")
```

</center>


The percent of samples tracked within each block can be seen below:

<center>

```{r print percent tracked}
perc_tracked_block %>%
  rename(trial = remember_loop_this_trial_n) %>%
  kable %>%
  kable_styling("striped") %>% 
  scroll_box(width = "500px", height = "200px")
```

</center>

### Gaze Position

```{r}
perc_on_screen <- combined_n %>%
  filter(block != 'response', !is.na(comb_gaze_x),!is.na(comb_gaze_y)) %>%
  summarize(avg_within = round(sum(between(comb_gaze_x,0,1920) & between(comb_gaze_y,0,1080))/n()*100,2))

perc_in_stim <- combined_n %>%
  filter(block == 'stimulus', !is.na(comb_gaze_x), !is.na(comb_gaze_y)) %>%
  summarize(avg_within = round(sum(between(comb_gaze_x,540,1380) & between(comb_gaze_y,0,540))/n()*100,2))
```

All gaze position data is taken after the instructions were completed. Presented data is average gaze position as given by the eyetracker. Samples where no eyetracking data is recorded are removed from the overall count.

**Note**: Hexes containing less than 0.1% of the total number of samples were excluded from all hexbin plots.

- % of time participant was gazing on screen: `r perc_on_screen$avg_within`%.

```{r define hexbin count func}
# This function will precompute the counts within each bin so bins with normalized values below a given cutoff will be removed from the plot altogether.
hexbin_count <- function(df, 
                          gaze_x = 'comb_gaze_x', 
                          gaze_y = 'comb_gaze_y',
                          xlim,
                          ylim,
                          nbins = 30,
                          cutoff = 0.001){
  
  hbin <- hexbin(df[[{{ gaze_x }}]],df[[{{ gaze_y }}]], xbnds = xlim, ybnds = ylim, xbins = nbins, IDs = TRUE)
  
  agg <- data.frame(hcell2xy(hbin),
                    cID = hbin@cell,
                    count = hbin@count) %>%
    mutate(ncount = count/sum(count)) %>%
    filter(ncount >= cutoff) %>%
    rename(hex_x = x,
           hex_y = y,
           hex_ncount = ncount) %>%
    tibble()
}
```

<center>

```{r screen gaze position}
screen_gaze_hist <- combined_n %>%
  filter(block != 'response', between(comb_gaze_x,0,1920) & between(comb_gaze_y,0,1080)) %>%
  hexbin_count(xlim = c(0,1920), ylim = c(0,1080)) %>%
  ggplot(aes(x = hex_x, hex_y, fill = hex_ncount*100,
             text = paste('x:', round(hex_x,0), '\n',
                          'y:', round(hex_y,0), '\n',
                          'percent:', round(hex_ncount*100,2),'%'))) +
  geom_hex(stat = 'identity') +
  scale_x_continuous(limits = c(0,1920)) +
  scale_y_reverse(limits = c(1080,0)) +
  scale_fill_viridis_c(option = 'inferno', limits = c(0.1,5), oob = oob_squish) +
  coord_fixed() +
  labs(title = 'Gaze Plot Over the Screen', x = '', y = '', fill = '% of samples') +
  c.theme()

ggplotly(screen_gaze_hist, tooltip = 'text')

rm(screen_gaze_hist)
```

</center>

- % of time participant was gazing within the stimulus area during stimulus blocks: `r perc_in_stim$avg_within`%.

<center>

```{r stim gaze position}
stim_hexbin <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,540,1380) & between(comb_gaze_y,0,540)) %>%
  hexbin_count(nbins = 40, xlim = c(540,1380), ylim = c(0,540))

stim_gaze_hist <- stim_hexbin %>%
  ggplot(aes(x = hex_x, y = hex_y, fill = hex_ncount*100,
             text = paste('x:', round(hex_x,0), '\n',
                          'y:', round(hex_y,0), '\n',
                          'percent:', round(hex_ncount*100,2),'%'))) +
  geom_hex(stat = 'identity') +
  xlim(540,1380) +
  scale_y_reverse(limits=c(540,0)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(0.1,5), oob = oob_squish) +
  labs(title = 'Gaze Within Stimulus Zone During Stimulus', x = '', y = '', fill = '% of samples') +
  c.theme()

ggplotly(stim_gaze_hist, tooltip = list('x','y','text'))
```

</center>

## Pupil Size

### Size During Fixation

Normalization of pupil size is done using the mean or median of the last `r wl` samples for which gaze was measured and within the screen coordinates. Pupil size can vary substantially from trial to trial, but within these samples, variance should be low. The following plots show the mean, median, min, max, and standard deviation of the pupil size within the window.

```{r fix pupil size, fig.cap = "The mean is shown as a red triangle while the median is shown as a black dot. Standard Deviation is plotted on the median, but is the same for both mean and median values."}
fix_df %>%
  rowid_to_column() %>%
  mutate(facet_row = cut(rowid-1, breaks = 3, labels = FALSE, right = FALSE)) %>%
  select(-rowid) %>%
  ggplot(aes(x = remember_loop_this_trial_n)) +
  geom_point(aes(y = fix_median_comb_pupil_size)) + 
  geom_point(aes(y = fix_mean_comb_pupil_size), 
             shape = 24, 
             fill = 'red') +
  geom_errorbar(aes(ymin = fix_median_comb_pupil_size - fix_sd_comb_pupil_size,
                    ymax = fix_median_comb_pupil_size + fix_sd_comb_pupil_size),
                width = 0.7) +
  geom_text(aes(y = fix_median_comb_pupil_size + fix_sd_comb_pupil_size + 100,
                label = as.character(missing_samples)),
            size = 3) +
  labs(x = 'Trial Number', 
       y = 'Raw Pupil Size', 
       title = 'Mean, Median, and SD of Pupil Size During Fixation Window') +
  facet_wrap(~facet_row, scales = "free_x", nrow = 3) +
  c.theme() +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        plot.title = element_text(size = 18),
        axis.text.x = element_text(size = 7))
```


### Distribution of Pupil Sizes

Eyelink reports pupil data from left and right eyes as well as the average of the two. The preprocessing pipeline performs mean and median normalization on all 3 measures relative to  fixation baseline. The following plots show the distribution of pupil sizes for samples where the participant has their gaze on the screen during the stimulus blocks. Values above and below the wiskers represent how many outliers exist on each side of the given boxplot. Outliers are defined as being beyond 1.5 times the interquartile range from the upper or lower quartile.

<center>

```{r pupil size histograms}
pupil_dens <- function(df,plot_title,remove_outliers = TRUE){
  
  df <- df %>%
    pivot_longer(everything(),
                 names_to = 'type',
                 values_to = 'size') %>%
    mutate(type = case_when(str_detect(type,'comb') ~ 'Combined',
                            str_detect(type,'left') ~ 'Left',
                            str_detect(type,'right') ~ 'Right'))
  
  if (remove_outliers){
    df.s <- df %>%
      group_by(type) %>%
      summarize(bp = boxplot.stats(size)$stats) %>%
      mutate(q = c('min','lower','med','upper','max')) %>%
      pivot_wider(names_from = q, values_from = bp)
    
    df.s <- df %>%
      left_join(df.s, by = 'type') %>%
      mutate(is.lower = size < min,
             is.higher = size > max) %>%
      group_by(type) %>%
      summarize(pos = sum(is.higher),
                neg = sum(is.lower)) %>%
      left_join(df.s, by = 'type')
      
      
    p <- df.s %>%
      ggplot(aes(x = type)) +
      geom_boxplot(mapping = aes(ymin = min,
                                 lower = lower,
                                 middle = med,
                                 upper = upper,
                                 ymax = max,
                                 fill = type),
                   stat = 'identity',
                   width = 0.2) +
      geom_text(aes(y = max, label = as.character(pos)),
                vjust = -0.3) +
      geom_text(aes(y = min, label = as.character(neg)),
                vjust = 1)
  } else {
    p <- df %>%
      ggplot(aes(x = type, y = size, fill = type)) +
      geom_boxplot(width = 0.2)
  }
  
  p +
    labs(x = '', y = 'Pupil Size', title = plot_title, fill = 'Eye') +
    c.theme() +
    theme(plot.title = element_text(size = 20),
          axis.title = element_text(size = 16),
          legend.position = 'none')
}

raw_p <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,0,1920), between(comb_gaze_y,0,1080)) %>%
  select(comb_pupil_size,left_pupil_size,right_pupil_size) %>%
  pupil_dens(plot_title = 'Raw Pupil Size')

mean_fix_p <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,0,1920), between(comb_gaze_y,0,1080)) %>%
  select(mean_comb_pupil_norm_fix, mean_left_pupil_norm_fix, mean_right_pupil_norm_fix) %>%
  pupil_dens(plot_title = 'Mean Fixation Normalized Pupil Size')

med_fix_p <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,0,1920), between(comb_gaze_y,0,1080)) %>%
  select(med_comb_pupil_norm_fix, med_left_pupil_norm_fix, med_right_pupil_norm_fix) %>%
  pupil_dens(plot_title = 'Median Fixation Normalized Pupil Size')

raw_p

mean_fix_p

med_fix_p
```
</center>

### Pupil Sizes During Stimuli

Median combined (combined left and right values) pupil size is plotted for each stimulus block as a function of epoch. Raw values are plotted followed by fixation-normalized values. Within stimulus blocks, patterns of change in pupil size are not different across the raw and two types of normalization, however the differences pupil size between blocks do differ across normalization. The extent to which they differ is dependent on the variance in pupil size during the chosen normalization block across samples.

```{r raw stimuli pupil sizes, fig.width = 12, fig.height= 8}
stim_df %>%
  ggplot(aes(x = epoch, y = stim_med_comb_pupil_size)) +
  geom_point(size = 2) + 
  facet_wrap(~remember_loop_this_trial_n) + 
  labs(x = 'Epoch', 
       y = 'Pupil Size (unitless)', 
       title = 'Raw Median Pupil Size Across Epochs Within Stimulus') +
  c.theme()
```

```{r fix norm stimuli pupil sizes, fig.width = 12, fig.height= 8}
stim_df %>%
  ggplot(aes(x = epoch, y = stim_med_comb_pupil_norm_fix)) +
  geom_point(size = 2) + 
  facet_wrap(~remember_loop_this_trial_n) + 
  labs(x = 'Epoch', 
       y = 'Pupil Size (unitless)', 
       title = 'Fixation-normalized Median Pupil Size Across Epochs Within Stimulus') +
  c.theme()
```


### Pupil Size and Gaze Position

Median combined pupil sizes for each bin are plotted as a function of gaze position during stimulus blocks. Only positions within the boundary of the stimulus area are plotted. Non-normalized median values are plotted first followed by fixation normalized values.

#### Raw Pupil Size

```{r define hebin_filter function}
# As opposed to hexbin_count, this function removes data from hexes with normalized counts < cutoff but returns the filtered data with the hex ID and hex X and Y posisitions added as columns for aggregation of other metrics
hexbin_filter <- function(df, 
                          gaze_x = 'comb_gaze_x', 
                          gaze_y = 'comb_gaze_y',
                          xlim,
                          ylim,
                          nbins = 30,
                          cutoff = 0.001){
  
  hbin <- hexbin(df[[{{ gaze_x }}]],df[[{{ gaze_y }}]], xbnds = xlim, ybnds = ylim, xbins = nbins, IDs = TRUE)
  
  agg <- data.frame(hcell2xy(hbin),
                    cID = hbin@cell,
                    count = hbin@count) %>%
    mutate(ncount = count/sum(count)) %>%
    filter(ncount >= cutoff) %>%
    rename(hex_x = x,
           hex_y = y,
           hex_ncount = ncount) %>%
    tibble()
  
  df <- df %>%
    mutate(cID = hbin@cID) %>%
    filter(cID %in% agg$cID) %>%
    left_join(agg, by = 'cID')
}
```

<center>

```{r raw pupil size gaze, fig.show='hold'}
stim_gaze_raw <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,540,1380) & between(comb_gaze_y,0,540)) %>%
  hexbin_filter(xlim = c(540,1380), ylim = c(0,540), nbins = 40) %>%
  group_by(cID) %>%
  summarize(hex_x = unique(hex_x),
            hex_y = unique(hex_y),
            pupil_med = median(comb_pupil_size),
            pupil_sd = sd(comb_pupil_size))

stim_gaze_pupil_size <-  stim_gaze_raw %>%
  ggplot(aes(x = hex_x, y = hex_y, fill = pupil_med)) +
  geom_hex(stat = 'identity') +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(540,0)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(300,550), oob = squish) +
  labs(title = 'Median Pupil Size During Stimulus', x = '', y = '', fill = 'Pupil Size') +
  c.theme()

stim_gaze_pupil_sd <- stim_gaze_raw %>%
  ggplot(aes(x = hex_x, y = hex_y, fill = pupil_sd)) +
  geom_hex(stat = 'identity') +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(540,0)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno', limits = c(0,100), oob = squish) +
  labs(title = 'Median Pupil SD', x = '', y = '', fill = 'Pupil SD') +
  c.theme()

ggplotly(stim_gaze_pupil_size)

ggplotly(stim_gaze_pupil_sd)

ggplotly(stim_gaze_hist, tooltip = c('text'))
```


</center>

#### Fixation Normalized 

<center>

```{r, fig.show='hold'}
stim_gaze_norm <- combined_n %>%
  filter(block == 'stimulus', between(comb_gaze_x,540,1380) & between(comb_gaze_y,0,540)) %>%
  hexbin_filter(xlim = c(540,1380), ylim = c(0,540), nbins = 40) %>%
  group_by(cID) %>%
  summarize(hex_x = unique(hex_x),
            hex_y = unique(hex_y),
            pupil_med = median(med_comb_pupil_norm_fix),
            pupil_sd = sd(med_comb_pupil_norm_fix))

stim_gaze_pupil_size_fix <- stim_gaze_norm %>%
  ggplot(aes(x = hex_x, y = hex_y, fill = pupil_med)) +
  geom_hex(stat = 'identity') +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(540,0)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Fixation Normalized Median Pupil Size', x = '', y = '', fill = 'Pupil Size') +
  c.theme()

stim_gaze_pupil_sd_fix <- stim_gaze_norm %>%
  ggplot(aes(x = hex_x, y = hex_y, fill = pupil_sd)) +
  geom_hex(stat = 'identity') +
  scale_x_continuous(limits = c(540,1380)) +
  scale_y_reverse(limits = c(540,0)) +
  coord_fixed() + 
  scale_fill_viridis_c(option = 'inferno') +
  labs(title = 'Fixation Normalized Median Pupil SD', x = '', y = '', fill = 'Pupil Size SD') +
  c.theme()

ggplotly(stim_gaze_pupil_size_fix)

ggplotly(stim_gaze_pupil_sd_fix)

```

</center>